---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---
IMI field study (2019) -- liver results

```{r load packages}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(devtools)
library(rstan)
library(rstantools)
library(bayesplot)
library(loo)
```

```{r read data}
d <- read_csv("/Users/kaitlyncampbell/Documents/USD/Chapter4_Brains_IMI/Field/UNL_imi_liver_data.csv")

# change to factor
d$Wetland_type <- as.factor(d$Wetland_type)
d$Sample_ID <- as.factor(d$Sample_ID)

# Add 0.000001 to imi brain values so it can be used in a gamma distribution (gamma models can't handle 0 values and one of the frogs had 0 ng/mg protein of imi in its brain)
d <- d %>% 
  mutate(Liver_imi_desnitro_ng_g_dwt = Liver_imi_desnitro_ng_g_dwt + 0.000001)

d <- d %>% 
  mutate(Brain_imi_pg_mg_protein = Brain_imi_pg_mg_protein + 0.000001)
```

# quick visualization 
```{r plot raw data}
ggplot(d, aes(x=Brain_imi_pg_mg_protein, y=Liver_imi_desnitro_ng_g_dwt, color=Sample_ID)) + geom_point()

ggplot(d, aes(x=Body_mass_g, y=Liver_imi_desnitro_ng_g_dwt)) + geom_point() + geom_smooth()

ggplot(d, aes(x=TL_mm, y=Liver_imi_desnitro_ng_g_dwt)) + geom_point() + geom_smooth()

ggplot(d, aes(x=Wetland_type, y=Liver_imi_desnitro_ng_g_dwt)) + geom_boxplot()
```

```{r prior simulation}
# density of raw data
plot(density(d$Liver_imi_desnitro_ng_g_dwt))
plot(hist(d$Liver_imi_desnitro_ng_g_dwt))
plot(hist(d$Brain_imi_pg_mg_protein))

# filter for just tile wetland animals to get an idea of the range of values
dt <- d %>% 
  filter(Wetland_type == 'Tile')
plot(density(dt$Liver_imi_desnitro_ng_g_dwt))

plot(hist(rexp(100, 0.25))) # range from 0-4; sounds reasonable


x.max = qgamma(0.999, shape=4.0, scale=0.5)
x = seq(from=0, to=x.max, by=x.max/1000)
dens = dgamma(x, shape=4.0, scale=0.5)
plot(x, dens, type='l')

# prior probability of this parameter being less than 5.0 or greater than 30.0 is about 0.0003 and 0.07, respectively:
pgamma(0.5, shape=5.0, scale=0.5, lower.tail=T) # 0.003659847
pgamma(8, shape=5.0, scale=0.5, lower.tail=F) # 3.624301e-09


y_true <- exp(-2) # exp(0) comes from the intercept prior of (0,0.5)
set.seed(1)
plot(density(rgamma(100, rate=0.25 / y_true, shape= 6))) # Values ranged from 0 to ~50 which is within the range of IMI_ole values (0 to ~25)
```

# try a model with a varying intercept (1|Wetland_type)
```{r}
m0.5 <- brm(Liver_imi_desnitro_ng_g_dwt ~ Brain_imi_pg_mg_protein + (1|Wetland_type), data = d, family = Gamma(link = "log"), 
          prior=c(prior(normal(-2, 0.05), class=Intercept),
                  prior(normal(-0.25, 0.25), class = b),
                  prior(gamma(1,3), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

# model checks
conditional_effects(m0.5) #liver conc 0-0.8
pp_check(m0.5, type = "boxplot", notch=FALSE)
pp_check(m0.5, type="hist")
pp_check(m0.5, type = "dens_overlay", resp = "Liver_imi_desnitro_ng_g_dwt", ndraws=100)
pp_check(m0.5, type = "dens_overlay", resp = "Brain_imi_pg_mg_protein", ndraws=100)
pp_check(m0.5, type = "dens_overlay", resp = "Intercept", ndraws=100)

# save model
save(m0.5, file = "/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m0.5.rda")

load("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m0.5.rda")
```

# adjust priors and re-run diff model
```{r}
m1 <- brm(Liver_imi_desnitro_ng_g_dwt ~ Brain_imi_pg_mg_protein + (1|Wetland_type), data = d, family = Gamma(link = "log"), 
          prior=c(prior(normal(-2, 0.25), class=Intercept),
                  prior(normal(-0.25, 0.25), class = b),
                  prior(gamma(1,3), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

# save
save(m1, file = "/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m1.rda")

load("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m1.rda")
```

# remove varying intercept and Brain_imi_pg_mg_protein as a variable
```{r m2}
# prior only model
m2_prior <- brm(Liver_imi_desnitro_ng_g_dwt ~ Wetland_type, data = d, family = Gamma(link = "log"), 
          prior=c(prior(normal(-2, 0.25), class=Intercept),
                  prior(normal(1, 2), class = b),
                  prior(gamma(6, 0.5), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE), sample_prior = "only")

conditional_effects(m2_prior)

m2 <- brm(Liver_imi_desnitro_ng_g_dwt ~ Wetland_type, data = d, family = Gamma(link = "log"), 
          prior=c(prior(normal(-2, 0.25), class=Intercept),
                  prior(normal(1, 2), class = b),
                  prior(gamma(6, 0.5), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

# save
save(m2, file = "/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m2.rda")

load("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m2.rda")

# model checks
print(m2)
conditional_effects(m2)
pp_check(m2, type = "boxplot", notch=FALSE)
pp_check(m2, type="hist")

pp_check(m2, type = "dens_overlay", resp = "Liver_imi_desnitro_ng_g_dwt", ndraws=100)
pp_check(m2, type = "dens_overlay", resp = "Intercept", ndraws=100)

d %>%
  tidybayes::add_predicted_draws(object = m2, ndraws = 250) %>%
  ungroup() %>%
  ggplot(aes(x = .prediction, group = .draw)) +
  geom_line(stat = 'density',
            alpha = 0.1,
            colour = 'blue') +
  geom_line(stat = 'density',
            data = d,
            mapping = aes(x = Liver_imi_desnitro_ng_g_dwt, group = NULL),
            colour = 'black',
            size = 1.5) +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(x = expression(paste('IMI des-nitro liver density ')),
       title = 'IMI des-nitro liver, actual versus predicted') 
```

# similar, but adjust priors
```{r m3}
m3 <- brm(Liver_imi_desnitro_ng_g_dwt ~ Wetland_type, data = d, family = Gamma(link = "log"), 
          prior=c(prior(normal(-2, 1), class=Intercept),
                  prior(normal(1, 2), class = b),
                  prior(gamma(6, 0.25), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

# save
save(m3, file = "/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m3.rda")

load("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/Liver_model_R_code/model_selection/m3.rda")

# model checks
print(m3)
conditional_effects(m3)
pp_check(m3, type = "boxplot", notch=FALSE)
pp_check(m3, type="hist")

pp_check(m3, type = "dens_overlay", resp = "Liver_imi_desnitro_ng_g_dwt", ndraws=100)
pp_check(m3, type = "dens_overlay", resp = "Intercept", ndraws=100)

pp_check(m3, type='stat', stat='mean')

d %>%
  tidybayes::add_predicted_draws(object = m3, ndraws = 250) %>%
  ungroup() %>%
  ggplot(aes(x = .prediction, group = .draw)) +
  geom_line(stat = 'density',
            alpha = 0.1,
            colour = 'blue') +
  geom_line(stat = 'density',
            data = d,
            mapping = aes(x = Liver_imi_desnitro_ng_g_dwt, group = NULL),
            colour = 'black',
            size = 1.5) +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(x = expression(paste('IMI des-nitro liver density ')),
       title = 'IMI des-nitro liver, actual versus predicted') 
```
# m3 = final model


# loo
```{r}
loo_m0.5 <- loo(m0.5, save_psis = TRUE, cores = 1)
print(loo_m0.5) # ok = 2, good = 8
plot(loo_m0.5, label_points = TRUE) # point 8 and 10
yrep <- brms::posterior_predict(m0.5)

bayesplot::ppc_loo_pit_overlay(d$Liver_imi_desnitro_ng_g_dwt, 
                    yrep = yrep, 
                    lw = weights(loo_m0.5$psis_object))

loo_m1 <- loo(m1, save_psis = TRUE, cores = 1)
print(loo_m1) # ok = 2, good = 8
plot(loo_m1, label_points = TRUE) # point 8 (ok) and 10 (ok)
yrep <- brms::posterior_predict(m1)

ppc_loo_pit_overlay(d$Liver_imi_desnitro_ng_g_dwt, 
                    yrep = yrep, 
                    lw = weights(loo_m1$psis_object))

loo_m2 <- loo(m2, save_psis = TRUE, cores = 1)
print(loo_m2) # ok = 1, good = 9
plot(loo_m2, label_points = TRUE) # point 8 (ok)
yrep <- posterior_predict(m2)

ppc_loo_pit_overlay(d$Liver_imi_desnitro_ng_g_dwt, 
                    yrep = yrep, 
                    lw = weights(loo_m2$psis_object))

loo_compare(loo_m0.5, loo_m1, loo_m2) # m0.5 > m1
```
     elpd_diff se_diff
m0.5   0.0       0.0  
m1    -0.1       0.1  
m2   -20.5       2.3

# extract posterior samples
```{r}
posts <- m3$data %>%  # uses the raw data contained in the model file
  modelr::data_grid(Wetland_type) %>%  # from modelr. creates a grid of data points to predict over
  tidybayes::add_epred_draws(m3)  # from bayesplot. for each point on the grid, samples a bunch of draws (i.e., iterations) of the outcome variable

posts
```

# summarize and plot the posteriors
```{r}
p_liver <- posts %>%
  ggplot() +
  geom_boxplot(aes(x=Wetland_type, y=.epred), 
            outlier.shape = NA, width = 0.1, 
            position = position_dodge(0.9)) +
  geom_jitter(data = m3$data, 
              aes(x=Wetland_type, y = Liver_imi_desnitro_ng_g_dwt), 
              shape=21, size=1.5, alpha=0.6, 
              width=0.05, fill="grey52") +
  theme_classic() +
  labs(x = "Wetland Type",
       y = "Desnitro-imidacloprid \nLiver Concentration (µg/g)",
       color = "Concentration (µg/L)") +
  theme(axis.text.x = element_text(color="black", size="10")) +
  theme(axis.text.y = element_text(color="black", size="10")) +
  theme(legend.title = element_text(face="bold", size="10"))

p_liver

#ggsave("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/New_figs/imi_trtp.tiff", p_liver, dpi=400, width=5, height=3, units="in")
```

# summary stats w/ 89% CI
```{r}
summary <- posts %>%
  group_by(Wetland_type) %>%
  #tidybayes::median_qi(.epred, .width = 0.89) %>% 
  tidybayes::mean_qi(.epred, .width = 0.89)

post_sum <- posts %>% 
  group_by(Wetland_type) %>% 
  summarize(median = median(.epred),
            mean = mean(.epred),
            sd = sd(.epred),
            low89 = quantile(.epred, probs = 0.055),
            high89 = quantile(.epred, probs = 0.945))

summary
```
# output:
  Wetland_type     .epred      .lower     .upper .width .point .interval
1 Reference    0.00000114 0.000000903 0.00000155   0.89 median qi   
2 Tile         1.97       1.57        2.51         0.89 median qi

# calc probability of a difference
```{r}
R <- posts %>% 
  filter(Wetland_type == "Reference") %>% 
  rename(R.epred = .epred)

T <- posts %>% 
  filter(Wetland_type == "Tile") %>% 
  rename(T.epred = .epred)

dd <- data.frame(R, T)

diff <- (T$T.epred - R$R.epred)
mean(diff) # 1.998381
quantile(diff,probs=c(0.055,0.945))   # 89% CI
sum(diff>0)/6000
```
# output:
    5.5%    94.5% 
1.573491 2.511698 

# plot!!
```{r}
# add colors
cp <- c("gray83", "grey55")

plot_liver <- ggplot() +
  geom_violin(data=posts, aes(x=Wetland_type, y=.epred, fill=Wetland_type), position = "dodge") +
  geom_boxplot(data=posts, aes(x=Wetland_type, y=.epred, fill=Wetland_type), outlier.shape = NA, width = 0.1, position = position_dodge(0.9)) +
  geom_jitter(data=d, aes(x=Wetland_type, y=Liver_imi_desnitro_ng_g_dwt), size=0.5, shape=1, width = 0.25) +
  scale_y_log10() +
  labs(x = "Wetland Type", 
       y = "Desnitro-imidacloprid \nLiver Concentration \n(ng/g dwt)",
       fill= "Wetland Type") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5),
        plot.caption=element_text(size=10)) +
  theme_classic() + 
  scale_fill_manual(values=cp) + 
  theme(plot.caption = element_text(hjust = 0)) +
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))
plot_liver

# save
ggsave("/Users/kaitlyncampbell/Documents/USD/Publications/IMI_field/New_figs/imi_liver_trt.tiff", plot_liver, dpi=400, width=5, height=3, units="in")
```

