---
title: "Untitled"
author: "Kaitlyn Campbell"
date: "5/25/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r load libraries}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(readr)
library(faintr)
library(devtools)
library(rstan)
library(rstantools)
library(readr)
library(tidybayes)
library(bayesplot)
```
```{r import data and manipulate}
my_data <- read_csv("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/my_data2.csv")
my_data <- select(my_data, -X1)

my_data <- my_data %>% 
  mutate(TL_mm = TL_cm*10)

my_data$Wetland_type <- as.factor(my_data$Wetland_type)
my_data$Site <- as.factor(my_data$Site)

bo <- my_data %>% 
  filter(Measurement == "1_bulbus_olf_length")
```

```{r}
# check levels
levels(my_data$Site)
levels(my_data$Wetland_type)

# Rename all levels
levels(my_data$Site) <- c("Acheson","Buffalo Lake","Habeger", "Lost Lake", "Pettigrew", "Volker")
levels(my_data$Wetland_type) <- c("Control","Tile")

# filter for one brain measurement to prevent duplicates for each individual in the dataset
bo <- my_data %>% 
  filter(Measurement == "1_bulbus_olf_length")

bo <- bo %>% 
  rename(type = "Wetland_type")
```

# model to determine if body mass differed between reference and tile wetland sites in 2019
```{r mass model}
m_mass1.1 <- brm(Body_mass_g ~ Wetland_type, data = bo, family = Gamma(link = "log"), 
          prior=c(prior(normal(2.5, 2), class=Intercept),
                  prior(normal(0, 2), class = b),
                  prior(gamma(0.01,0.01), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, control = list(adapt_delta = 0.999), 
          save_pars = save_pars(all = TRUE))
```

# Extract posteriors
```{r}
set.seed(4545)
post_1 <- posterior_samples(m_mass1.1)  # puts chains of model into data frame
head(post_1)
nrow(post_1) # 6000
```

# Compute averages for each treatment category
```{r}
as_tibble(post_1) %>% 
  mutate(iteration = 1:nrow(post_1))

# Reference
mu_ref_mass <- data.frame(value = exp(post_1$b_Intercept), type = "Reference", iter = 1:nrow(post_1)) 

# Tile
mu_tile_mass <- data.frame(value = exp(post_1$b_Intercept + post_1$b_Wetland_typetile), type = "Tile", iter = 1:nrow(post_1))

mu_mass <- rbind(mu_ref_mass, mu_tile_mass)
```

# summarize
# 89% and 95% CI
```{r}
summary <- mu_mass %>% 
  group_by(type) %>% 
  summarize(mean = mean(value),
            median= median(value),
            sd = sd(value),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945),
            low95 = quantile(value, probs = 0.025),
            high95 = quantile(value, probs = 0.975)) %>%
  mutate_if(is.numeric,round,2)
summary

view(summary)
```
## output:
  type       mean median    sd low89 high89 low95 high95
1 Reference  14.4   14.3  1.35  12.4   16.7  12.0   17.4
2 Tile       15.8   15.8  1.51  13.6   18.4  13.2   19.1

# differences between tile and reference sites?
```{r}
diff_ct <- mu_tile_mass$value - mu_ref_mass$value
mean(diff_ct) # 1.430934 g
quantile(diff_ct,probs=c(0.025,0.975)) # (-2.522099, 5.400463)
quantile(diff_ct,probs=c(0.055,0.945)) # (-1.633938, 4.653148)
sum(diff_ct>0)/6000 # 0.7686667
```
# Less than a 77% probability that there is a difference

# make plot
```{r}
bo$type2<-ifelse(bo$Wetland_type=="control", "Reference", "Tile")
bo$type2 <- as.factor(bo$type2)

# use light and dark grey to represent control vs tile
cp <- c("gray83", "grey55")

mass_p <- mu_mass %>%
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9)) +
  geom_point(data = bo, aes(x=type2, y=Body_mass_g, fill= type2), shape = 1, size = 1, position = position_jitterdodge(seed = 1, dodge.width =0.9)) +
  labs(x = "Site", 
       y = "Body Mass (g)",
       fill= "Wetland Type") +
    theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + 
  scale_fill_manual(values=cp) +
  theme(plot.caption = element_text(hjust = 0, size=8))
mass_p

#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Field/plots/mass_p.tiff", mass_p, dpi=400, width=5, height=3, units="in")
```


##### TL (total body length) ##### 
```{r m_tl5_mm model}
m_tl5_mm <- brm(TL_mm ~ Wetland_type + (1|Animal_ID), data = bo, family = Gamma(link = "log"), 
          prior=c(prior(normal(3, 3), class=Intercept),
                  prior(normal(0, 3), class = b),
                  prior(cauchy(0, 1), class= sd),
                  prior(gamma(0.01,0.01), class="shape")),
          iter = 3000 , warmup = 700, chains = 4, cores = 4,
          seed = 5, control = list(adapt_delta = 0.999), 
          save_pars = save_pars(all = TRUE))
```

# Extract posteriors
```{r}
set.seed(4545)
post_2 <- posterior_samples(m_tl5_mm)  # puts chains of model into data frame
head(post_2)
nrow(post_2) # 9200
```
# Compute averages for each treatment category
```{r}
as_tibble(post_2) %>% 
  mutate(iteration = 1:nrow(post_2))

# reference wetlands
mu_tl_ref <- data.frame(value = exp(post_2$b_Intercept), type = "Reference", iter = 1:nrow(post_2)) 

# tile wetlands
mu_tl_tile <- data.frame(value = exp(post_2$b_Intercept + post_2$b_Wetland_typetile), type = "Tile", iter = 1:nrow(post_2)) 

mu_tl <- rbind(mu_tl_ref, mu_tl_tile)
```

# get summaries
```{r}
mu_tl_summary <- mu_tl %>% 
  group_by(type) %>% 
  summarize(mean = mean(value),
            median= median(value),
            sd = sd(value),
            low95 = quantile(value, probs = 0.025),
            high95 = quantile(value, probs = 0.975),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945)) %>%
  mutate_if(is.numeric,round,2)

mu_tl_summary
```
## output:
  type       mean median    sd low95 high95 low89 high89
1 Reference  57.7   57.7  2.05  53.8   61.9  54.5   61.1
2 Tile       60.8   60.7  2.06  56.8   64.9  57.5   64.2

# differences?
```{r}
diff_ct_tl <- mu_tl_tile$value - mu_tl_ref$value
mean(diff_ct_tl) # 3.020575 mm
quantile(diff_ct_tl,probs=c(0.025,0.975)) # (-2.490823, 8.602962)
quantile(diff_ct_tl,probs=c(0.055,0.945)) # (-1.542854, 7.578885)
sum(diff_ct_tl>0)/9200 # 0.8569565
```

# Make plot
```{r}
# use light and dark grey to represent control vs tile
cp <- c("gray83", "grey55")

bo$type2<-ifelse(bo$Wetland_type=="control", "Reference", "Tile")
bo$type2 <- as.factor(bo$type2)

tl_p <- mu_tl %>%
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9)) +
  geom_point(data = bo, aes(x=type2, y=TL_mm, fill= type2), shape = 1, size = 1, position = position_jitterdodge(seed = 1, dodge.width =0.9)) +
  labs(x = "Wetland Type", 
       y = "Total Body Length (mm)",
       fill= "Wetland Type") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + 
  scale_fill_manual(values=cp) +
  theme(plot.caption = element_text(hjust = 0, size=8))
tl_p

#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Field/plots/tl_p.tiff", tl_p, dpi=400, width=5, height=3, units="in")
```

